---
title: "SSI Final Project Code Notebook"
output:
  html_document:
    df_print: paged
---

This is the R notebook for all code related to my project for SOSC 13200. Any images in the final write up were generated below. 

```{r}
# packages and data import
library(ggplot2)
dat <- read.csv("C:/Users/kathi/Downloads/anime_ratings.csv")
```


Here, we change the highest_mal_rating column from chrs to doubles. Then, we remove any rows which got NA values in the process. Finally, we remove ' *', which I used for marking shows that I'm not entirely caught up with yet. 
```{r warning=FALSE}
# clean data
dat$highest_mal_rating <- as.double(dat$highest_mal_rating)
dat <- dat[complete.cases(dat), ]
dat$anime_name <- gsub(" \\*", "", dat$anime_name)
```


## Part 1

First, we briefly summarize the data.
```{r}
# preview data
str(dat)
```

Here are the means for each column in the dataframe.
```{r}
# get mean values across df
numeric_columns <- sapply(dat, is.numeric)
means <- colMeans(dat[, numeric_columns], na.rm = TRUE)
medians <- apply(dat[, numeric_columns], 2, median, na.rm = TRUE)
means
medians
```

This is my attempt at making a continuous histogram to visualize rating distributions between me and MAL.
```{r}
ratings_data <- data.frame(
  Source = c(rep("My Ratings", length(dat$rating)), 
             rep("MAL Ratings", length(dat$highest_mal_rating))),
  Ratings = c(dat$rating, dat$highest_mal_rating)
)

# create overlapped density plots
ggplot(ratings_data, aes(x = Ratings, fill = Source)) +
  geom_density(alpha = 0.4) +
  labs(x = "Score", y = "Frequency", title = "Rating Distributions (Me vs MyAnimeList)") +
  scale_fill_manual(values = c("My Ratings" = "green", "MAL Ratings" = "yellow")) +
  theme_minimal()
```


## Part 2

first code
```{r}

```

